\documentclass{article}
\author{Sam Nolan and Michael Smith}
\title{Project Mini Drone Charter}

\begin{document}
  \maketitle

  \section{Introduction}
  \subsection{Brief project description}
  The project is to utilise a small group of nano-quadcopters in conjunction with the VIVE lighthouse indoor positioning system. 

  The system will be used to create light art using long exposure photography controlled 
  using a VIVE controller or pre-defined path. These drones may also interact with the VXLab 
  baxter robot (a.k.a. Rosie) as a landing platform and artistic subject.

  \subsection{Brief description of technical environment}
  We will be using 4 Bitcraze Crazyflie drones, controlled by Python scripts. 
  As well as lighthouse posititioning modules provided by the VX Labs

  \subsection{Estimated level of complexity}
  The main sources of complexity in this project will be working with communicating to the 
  drones and integrating it with the lighthouse positioning system. As well as decoding the SVGs
  to fly the drone in preset paths.

  This will take a moderate amount of complexity to create.

  \subsection{Estimated benefits/Problems it solved}
   
  This project will benefit the VX labs by providing promotional material to encourage other
  students to complete projects there. The promotional material will be in the form of light
  paintings, photography and videos that demonstrate the capabilities of the lab.

  \section {Technical Environment}

  The hardware environment will be using:
  4x Bitcraze Crazyflie
  2x lighthouse positioning modules (for VIVE)
  4x Lighthouse deck for Crazyflie 
  4x LED deck for Crazyflie 
  1x Baxter robot (Rosie)
  Various accessories such as chargers, batteries, propellers, controllers etc.

  These items were chosen due to availability within the lab.

  Software environment will be:

  Python as the main programming language. Chosen because this is the language used by the
  drone libraries.
   
  GitHub as source control, because GitHub is the most popular source control mechanism 
  available.

  \section {Overall Architecture}


  \section {System architecture}

  \subsection {Functionalities}
  
  \section {Database Architecture}

  Not applicable

  \section {Implementation Instructions}
  
  \section {Non-functional specifications}
  \section {Summary of test results}
  \section {Known Issues and Risks}

  \section {Other considerations}
  
\end{document}
